Algorithmic model for N-GREEN optical ring

### 2017-10-23 Papier NGreen/model.tex
pull dessin

	The source code int C of the simulator used for our experimental results is available on the \href{https://github.com/Mael-Guiraud/Ngreen.git}{ author's github page}.
	\subsection{Initialisation}
	First, we need to put coherent parameters , considering the model. For instance, with the parameters of NGREEN, we can not set more than 10 antennas on the ring. 
	The ring is modeled by a table of packets.

@@

	We then, for each antenna, initialize the first date $t$ on which the antenna send some traffic. The antenna will then send a message every 10 slots after $t$, during a fixed total time, depending of the throughput of the antenna.
	 In the Insertion Policy models, this date $t$ is randomly drawn with the rand() functions of stdlib. In the Reservation model, this date $t$ is set by the scheduling algorithms described in sec~\ref{det}.

>>>>

	The source code int C of the simulator used for our experimental results is available on the \href{https://github.com/Mael-Guiraud/Ngreen.git}{ author's github page}.
	\subsection{Initialisation}
	First, we need to put coherent parameters , considering the model. For instance, with the parameters of NGREEN, we can not set more than 10 antennas on the ring. 
	The ring is modeled by a circular table of struct packets.

@@

	We then, for each antenna, initialize the first date $t$ on which the antenna send some traffic. The antenna will then send a message every 10 slots after $t$, during a fixed total emission time, depending of the throughput of the antenna.
	 In the Insertion Policy models, this date $t$ is randomly drawn with the rand() functions of stdlib. In the Reservation model, this date $t$ is set by the scheduling algorithms described in sec~\ref{det}.
